%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[12pt, a4paper]{awesome-cv}

\usepackage{hyperref}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo{./examples/profile.png}
\name{Etienne}{CARRIERE}
\position{Site Reliability Engineer}
\address{Bourg la Reine, Hauts de Seine, France}

\mobile{(+33)6 95 30 23 34}
\email{etienne.carriere@gmail.com}
%\dateofbirth{January 1st, 1970}
%\homepage{www.posquit0.com}
%\github{Etienne-Carriere}
\linkedin{etienne-carriere-cloud}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{medium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {Sep 2024}
  {Etienne CARRIERE~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%-------------------------------------------------------------------------------

\newcommand*{\stack}[1]{
   \textbf{Stack} : #1
}

\cvsection{Experiences}
\vspace{-4mm}
\begin{cventries}
  \cventry
    {Senior Software developer} 
    {Datadog} 
    {Paris} 
    {Oct. 2018 - Now} 
    {
      \begin{cvitems} 
	    \item{Develop a load testing services so that, with coordination with chaos engineering services, it is possible to inject load while chaos disruptions are made} 
		\item{Migration from a python monolith handling more than 2k endpoints and 20k req/s to golang micro-services} 
		\begin{itemize}
		  \item{ Migrate the routes handled by our team that serves around 1k req/s}
		  \item{Support other teams to migrate their routes}
		\end{itemize}
		\item{Optimize cloud hosting costs by 30\% on a perimeter of 3 M\$/year}
		\item{Mentor 2 interns that joined our team at Datadog after their interships} 
		\item{Prepare with the team manager the quarter plannning of the team}
		\item{\stack{Kubernetes, Terraform, Datadog, Temporal. Development in Golang and Python}}
      \end{cvitems}
    }
	
  \cventry
    {DevOPS Architect} 
    {Société Générale} 
    {Paris} 
    {Oct. 2018 - Aug. 2023} 
    {
	  Build a private cloud for internal needs of Societe generale
	  \vspace{4.0mm}
      \begin{cvitems} 
        \item{Design, implement and maintain distributed tracing solution based on Jaeger/Opentracing/ElasticSearch}
		\item{Define, implement and maintain a Terraform provider for the private cloud : more than 70 resources and 30 datasources}
		\item{Design an ”Heroku for the project solution” based on Kubernetes for the 20 teams building the private cloud platform}
		\item{Develop a Kubernetes controllers for cert-manager to integrate our internal PKI API}
		\item{\stack{Terraform, Kubernetes, Ansible, Jaeger, Opentracing, ElasticSearch, Influx, Flink. Development in Python, Java and Golang. PoC with ClickHouse}}
      \end{cvitems}
    }
	
  \cventry
    {(First|Lead) DevOps} 
    {Datadome} 
    {Paris} 
    {Jun. 2017 - Sep. 2018} 
    {
	  First devops in a anti scraping/scalping startup. I arrived as 6th engineer
	  \vspace{4.0mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Automate deployment of Datadome infrastructure in 10 AWS regions with Terraform. The first 3 regions were built manually, I automated the deployment on the new regions}
		\item { Optimize AWS hosting costs of AWS infrastructure by 30\% (right-sizing resources, delete unused resources and optimize application to decrease outgoing network traffic}
		\item { Management of a mid-sized ElasticSearch cluster (1 billion document in-gested a day / 50 Tbytes stored)}
		\item {	Development of lowlevel application stack (mainly in Python and golang)}
		\item { \stack{ AWS, Azure, Ansible, Terraform, Centos, ElasticSearch, Docker, InfluxDB, Flink. Development in Java, Python and Golang}}
      \end{cvitems}
    }

  \cventry
    {DevOps Architect} 
    {French Ministry of Defense} 
    {Paris} 
    {Jan. 2016 - May. 2017} 
    {
	 Project \href{https://www.programmevitam.fr/}{Vitam} : Development of an \href{https://github.com/ProgrammeVitam/vitam}{open-source} long term digital archiving solution for French public organisations
	 \vspace{4.0mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item{ Design of deployment architecture (RPM/Deb packages)}
	   \item{ Development of a software generating an Archival Package in the SEDA Archival format (XML format used by archivists to handle metadatas)}
	   \item{ Manage the operational relation with the private cloud provider (Openstack provided by French Ministry of Agriculture)}
	   \item{ Manage the relation with the ”clients” of the project : Ministry of the Culture, Ministry of the Foreign relations, Ministry of Defence}
	   \item{ \stack{ Centos, Openstack, Ansible, Docker, MongoDB, ElasticSearch, Kibana, Consul. Development in Java, Python}}
      \end{cvitems}
    }
	
   \cventry
    {Technical Architect / Technical Project Manager} 
    {French Ministry of Finance : Transversal Human Resource ad-hoc structure} 
    {Paris} 
    {Jan. 2013 - Dec. 2015} 
    {
      \begin{cvitems} 
        \item {Physical design of 2 datacenters to host the transversal human resource system for public servants}
		\item {Design and manage the deployment of transversal services (Virtualization,DRP, Audit trail, file exchange service)}
		\item {Define and maintain the technical framework and the service portfolio}
		\item {\stack{ RHEL, KVM, F5, Tomcat, HR Access, GLPI, Graylog, Ansible}}
      \end{cvitems}
    }

  \cventry
    {Technical Architect Consultant} 
    {Solucom (now Wavestone)} 
    {Paris} 
    {Oct. 2007 - Dec. 2012} 
    {
      \begin{cvitems}
        \item {Design of technical architecture}
		\begin{itemize}
			\item {2011-2012 : Sita (part of Engie) : Define the new HR/Payroll system}
			\item {2011-2012 : French Ministry of finances : Define a new HR system for public servants}
			\item {2010-2011 : Cité des Sciences et de l’industrie : Define the new HR/Payroll system}
			\item {2009-2011 : Crédit Agricole : Design the intranet}
			\item {2007-2009 : Société Générale : Rework the online banking site}
		\end{itemize}
		\item{Technical Audits}
		\begin{itemize}
			\item {2011 : Peugeot (part of PSA) : Audit of the aftersales portal}
			\item {2010 : Snemca (part of Safran) : Audit of differents application}
			\item {2010 : SFR : Audit of the www.sfr.fr site}
		\end{itemize}
		\item {Datacenter relocation : Moving and consolidate european datacenters in a central datacenter}
      \end{cvitems}
    }
\end{cventries}

\cvsection{Education}
	\vspace{-4mm}	
	\begin{cventries}
	  \cventry
		{Engineer Degree} 
		{Ecole supérieure d’électricité (Supélec)} % Institution
		{Gif sur Yvette} 
		{2004 - 2007} 
		{
		  Leading school of engineering in the field of energy,computer science and data processing
		}
	  \vspace{4mm}
	  \cventry
		{Preparatory years years for the competitive examination for entry in the French ’Grandes Ecoles’} 
		{Lycée Strasbourg} 
		{Strasbourg} 
		{2001 - 2004}
		{}
	\end{cventries}

\cvsection{Skills}
	\begin{cvskills}
	  \cvskill{IaaS} {AWS, Openstack}
	  \cvskill{Infra as Code} {Terraform, Ansible}
	  \cvskill{Container}{Kubernetes, Docker} 
	  \cvskill{SQL DBMS}{ PostgreSQL, MySQL/MariaDB}
	  \cvskill{NoSQL DBMS} {ElasticSearch, InfluxDB, Clickhouse}
	  \cvskill{Programming}{Java,Go, Python} 
	  \cvskill{Framework/Libraries}{Java : Jetty, hibernate / Go : http.Server,chi,go-migrate / Python : Gunicorn,Flask, Django }
	\end{cvskills}
\end{document}